\chapter{Conclusion}

\paragraph{} First, we describe the unique activity map under various kind of input and various kind of convergent connection rules.  We then show the increase in output firing rate when feedforward connection strength increase and when the synchronization level in input increase. 
We demonstrate that in Uniform-Uniform convergent rule(UU) has highest response gain from static input to oscillating input when compare to other convergent rules.  
Finally, we reveal that the UU rule has highest number of induced spike gain and it is highly dependent on phase of input oscillation. The explanation on why the UU rule is most sensitive to synchronized input based on idea of temporal summation was also introduced. 

What does it mean?
Successfully regenerate experimental results with computational simulation
The simulation shows functional connection between thalamus and motor cortex in the real animal
What hypotheses were proved or disproved?
We can make computational simulation which resemble the experimental data
The T-Type calcium channel generate bursting behavior of single cell
The neural population are highly synchronized during bursting behavior
The high synchronization level in neural population can transfer information from one layer to another layer
What did I learn?
I can make computational model that can regenerate experimental data and I can use it to predict new properties of neural system
Why does it make a differences?
The simulation predicts functional connection between VL and M1 neuronal layers
The simulation suggest that reverse testing of KO cells to resemble WT can also drive motor command in M1. The finding suggests that the bursting is the important factor for high synchronization level of neural population and it is the key for neural network to transfer data from VL to M1

Add a new, higher level of analysis
Indicate explicitly the significance of the work
This work shows the potential of using computational simulation to regenerate experimental data in silico and employ it to manipulate properties of neuron network that are hard to do in the experiments and use it to predict new hypothesis
